%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage[english]{babel}

\input{header}

% DOCUMENT
\begin{document}
\reversemarginpar
{\LARGE Juan Hernández Babón}\\[0.25cm]
\href{mailto:juan.hernandez.babon@gmail.com}{juan.hernandez.babon@gmail.com}\\
\href{https://github.com/jhbabon}{https://github.com/jhbabon}\\

%%\hrule
\section*{Studies}

\textbf{Bachelor's Degree in Computer Science and Information Technology}. The degree was obtained at the Technical College of Computer Science at the University of Valladolid, Spain.

%%\hrule
\section*{Technical Skills}

I am specialized in web development, with backend development as my strength. I also have experience with the rest of the web stack, from the frontend development to server administration.

I am fully proficient with: Ruby (Rails), JavaScript (jQuery), HMTL, CSS, bash, zsh, Database Management Systems (SQL: PostgreSQL, MySQL; NoSQL: Redis), web servers (Apache, NginX) and continuous integration.

I am competent with: PHP, Python and C.

I work comfortably with UNIX systems (Mac OS X, and many flavours of Linux). My editor of choice is VIM, and I use Git as a source version control system for almost everything.

\section*{Motivation}

I care about software. I always try to make software that is helpful for the user and easy for other developers to maintain. I think that is the core idea of any development: to make software that is enjoyable at all levels, not a pain. I now that the world of development moves fast. That's why I always try to learn about new methodologies and technologies.

\section*{Profesional Experience}

\noindent\years{2013 - present} I currently work at \textbf{Xing}, in Barcelona, as a backend developer. I'm part of a team in charge of three applications focused in job offers and advertisement for companies. Our main goal is to provide the maximum visibility of those job offers for any job seeker that could come from Google or inside the \textbf{Xing} network. All the development is focused in a common Ruby on Rails stack: message queues (RabbitMQ), cache systems (Memcached and Redis), multiple development environments, internal APIs, etc.\\[.2cm]
\noindent\years{2012 - 2013} I worked at \textbf{Wuaki.tv}, part of the \textbf{Rakuten Group}, in Barcelona, as a backend developer using Ruby. \textbf{Wuaki.tv} is an ondemand video store, specialized in movies and tv shows. The biggest challenge for this system is to serve all the content to the main web app and all the devices connected to the service API, like Smart TV apps and tablets. We had resolved problems like: scalability of the system, management of diferent development environments for each kind of device, deploy of small and cooperative components, integration with other systems, build an architecture oriented to small services, implement queue systems, and so on.\\[.2cm]
\noindent\years{2011 - 2012} I worked at Gnuine, in Barcelona, as a web developer and project leader using Ruby on Rails and the open sourced CMS Ubiquo. I was a member of the team that develops the website for \textbf{FC Barcelona}. I worked on other projects as a Ruby developer, creating APIs for communication between applications. I had also been in charge of the packaging of a PhoneGap application for Android and iOS, and its integration with push notification systems of each of that platforms.\\[.2cm]
\noindent\years{2011} I worked for 3 moths as a PHP developer at Alt120, in Barcelona. I used the PHP framework Yii and jQuery.\\[.2cm]
\noindent\years{2009 - 2010} I was responsible for the web projects, in Ruby and PHP, and the administration of the Linux servers of the IBECON 2003 S.L.\\[.2cm]
\noindent\years{2008 - 2009} I developed a web application with the framework PHP Symfony for my Final Year Project. The application was created as a job for the CARTIF foundation, which used it for an internal project investigation.


\begin{center}
{\scriptsize  Updated at: \today\- •\- \href{https://raw.github.com/jhbabon/cv/master/cv_en.pdf}{Download the latest version of this document}\- •\- Document writted with \href{http://nitens.org/taraborelli/cvtex}{\fontspec{Palatino}\XeTeX}}
\end{center}

\end{document}
